\documentclass[11pt]{article}

\usepackage[
    left=1.0in,
    right=1.0in,
    top=1.0in,
    bottom=1.0in,
    paperwidth=8.5in,
    paperheight=11in,
]{geometry}

%\usepackage[render]{pdf_poker}
\usepackage{pdf_poker}

\usepackage{parskip}
\usepackage{tabularray}
\usepackage{listings}
\lstset
{
    language=[LaTeX]TeX,
    breaklines=true,
%    basicstyle=\tt\small,
    basicstyle=\tt,
    keywordstyle=\color{blue},
    identifierstyle=\color{magenta},
}


\begin{document}

\title{pdf\_poker for \LaTeX{}}

\author{Christopher Donham}

\date{March 26, 2025\\v1.0}

\maketitle

\centerline{
\begin{tikzpicture}
  \node (img1) {\rotatebox{60}{\CardTenClubs[0.5]}};
  \node (img2) at (img1.east) [xshift=-0.7cm, yshift=0.6cm] {\rotatebox{30}{\CardJackDiamonds[0.5]}};
  \node (img3) at (img1.east) [xshift=0cm, yshift=0.75cm] {\CardQueenClubs[0.5]};
  \node (img4) at (img1.east) [xshift=0.5cm, yshift=0.5cm] {\rotatebox{-30}{\CardKingHearts[0.5]}};
  \node (img5) at (img1.east) [xshift=1cm, yshift=0cm] {\rotatebox{-60}{\CardAceSpades[0.5]}};
\end{tikzpicture}}

\section{Introduction}

I am a statistics teacher and use pdflatex with Beamer to create
slides for my lessons.  Playing cards are commonly used to explain
probability and feature in some of my slides.  A fine library of
playing cards is available using pstricks.  However, Beamer, pdflatex and
pstricks do not interact well.  I also occasionally find other times
when packages I am using in pdflatex do not allow me to use pstricks.
I wrote this package so that I could use playing cards without having
to fight with pstricks.  

Currently, the package provides the 52 that comprise a standard deck
of cards.  There is no provision for drawing the back of a card.
There are currently no jokers or other special cards.

\vspace*{\baselineskip}

\begin{centering}
\CardAceSpades[0.3]
\CardTwoSpades[0.3]
\CardThreeSpades[0.3]
\CardFourSpades[0.3]
\CardFiveSpades[0.3]
\CardSixSpades[0.3]
\CardSevenSpades[0.3]
\CardEightSpades[0.3]
\CardNineSpades[0.3]
\CardTenSpades[0.3]
\CardJackSpades[0.3]
\CardQueenSpades[0.3]
\CardKingSpades[0.3]

\CardAceHearts[0.3]
\CardTwoHearts[0.3]
\CardThreeHearts[0.3]
\CardFourHearts[0.3]
\CardFiveHearts[0.3]
\CardSixHearts[0.3]
\CardSevenHearts[0.3]
\CardEightHearts[0.3]
\CardNineHearts[0.3]
\CardTenHearts[0.3]
\CardJackHearts[0.3]
\CardQueenHearts[0.3]
\CardKingHearts[0.3]

\CardAceDiamonds[0.3]
\CardTwoDiamonds[0.3]
\CardThreeDiamonds[0.3]
\CardFourDiamonds[0.3]
\CardFiveDiamonds[0.3]
\CardSixDiamonds[0.3]
\CardSevenDiamonds[0.3]
\CardEightDiamonds[0.3]
\CardNineDiamonds[0.3]
\CardTenDiamonds[0.3]
\CardJackDiamonds[0.3]
\CardQueenDiamonds[0.3]
\CardKingDiamonds[0.3]

\CardAceClubs[0.3]
\CardTwoClubs[0.3]
\CardThreeClubs[0.3]
\CardFourClubs[0.3]
\CardFiveClubs[0.3]
\CardSixClubs[0.3]
\CardSevenClubs[0.3]
\CardEightClubs[0.3]
\CardNineClubs[0.3]
\CardTenClubs[0.3]
\CardJackClubs[0.3]
\CardQueenClubs[0.3]
\CardKingClubs[0.3]

\end{centering}

\vspace*{\baselineskip}

\section{Installation}

The files needed to install this package consist of the the
\textbf{pdf\_poker.sty} file and the files in the \textbf{images
  directory}.  The images are the center portion of the face cards.
There are currently two versions of each image: 1) a tex version that
will render the face card image using tikzpicture, and 2) a png
version that is a pre-rendered image of the face card generated from
the tex version.  Technically, you do not need both version of each
image if you will only be using one of the operating modes of the
package.

\section{Usage}

The default operation of the package uses the pre-rendered versions of
the face cards.  This introduces a dependence on the graphicx package.
If the pre rendered versions of the face card images are insufficient
for your application, then the ``render'' flag will cause the package
to draw all face cards using tikzpicture.  Rendering the cards with
tikzpicture is significantly slower than using the pre-rendered
versions.

\begin{minipage}{0.5\linewidth}
\begin{lstlisting}
\usepackage{pdf_poker}
\end{lstlisting}
\end{minipage}
\begin{minipage}{0.5\linewidth}
  Example using typical, faster, image mode.
\end{minipage}
\begin{minipage}{0.5\linewidth}
\begin{lstlisting}
\usepackage[render]{pdf_poker}
\end{lstlisting}
\end{minipage}
\begin{minipage}{0.5\linewidth}
  Example using slower, memory intensive, rendering mode.
\end{minipage}

Each card has an optional scale factor to increase or decrease the size
of the card.
\vspace*{0.5\baselineskip}

\centerline{\begin{tblr}{width={0.9\linewidth}, colspec={X[c]X[c]X[c]}}
\tt\textbackslash CardJackHearts[0.3] & 
\tt\textbackslash CardJackHearts[0.45] & 
\tt\textbackslash CardJackHearts[0.6] \\
\CardJackHearts[0.3] & \CardJackHearts[0.45] & \CardJackHearts[0.6] \\
\end{tblr}}

Shown below are the names for all of the cards in the deck.
\vspace*{\baselineskip}

\bgroup\tt
\centerline{\begin{tblr}{width={0.9\linewidth},rowsep=1pt,colspec={XXXX}}
\textbackslash CardAceSpades   & \textbackslash CardAceHearts   & \textbackslash CardAceDiamonds   & \textbackslash CardAceClubs \\
\textbackslash CardTwoSpades   & \textbackslash CardTwoHearts   & \textbackslash CardTwoDiamonds   & \textbackslash CardTwoClubs \\
\textbackslash CardThreeSpades & \textbackslash CardThreeHearts & \textbackslash CardThreeDiamonds & \textbackslash CardThreeClubs \\
\textbackslash CardFourSpades  & \textbackslash CardFourHearts  & \textbackslash CardFourDiamonds  & \textbackslash CardFourClubs \\
\textbackslash CardFiveSpades  & \textbackslash CardFiveHearts  & \textbackslash CardFiveDiamonds  & \textbackslash CardFiveClubs \\
\textbackslash CardSixSpades   & \textbackslash CardSixHearts   & \textbackslash CardSixDiamonds   & \textbackslash CardSixClubs \\
\textbackslash CardSevenSpades & \textbackslash CardSevenHearts & \textbackslash CardSevenDiamonds & \textbackslash CardSevenClubs \\
\textbackslash CardEightSpades & \textbackslash CardEightHearts & \textbackslash CardEightDiamonds & \textbackslash CardEightClubs \\
\textbackslash CardNineSpades  & \textbackslash CardNineHearts  & \textbackslash CardNineDiamonds  & \textbackslash CardNineClubs \\
\textbackslash CardTenSpades   & \textbackslash CardTenHearts   & \textbackslash CardTenDiamonds   & \textbackslash CardTenClubs \\
\textbackslash CardJackSpades  & \textbackslash CardJackHearts  & \textbackslash CardJackDiamonds  & \textbackslash CardJackClubs \\
\textbackslash CardQueenSpades & \textbackslash CardQueenHearts & \textbackslash CardQueenDiamonds & \textbackslash CardQueenClubs \\
\textbackslash CardKingSpades  & \textbackslash CardKingHearts  & \textbackslash CardKingDiamonds  & \textbackslash CardKingClubs \\
\end{tblr}}
\egroup

\section{Requests for Enhancement}

RFE's for the future include:

\begin{itemize}
\item Draw the back of a card.

\item The code is fragile because the symbol for diamonds and hearts
  comes from a different font than the clubs and spades.  Unfortunately,
  the symbols are slightly different sizes resulting in a hard coded
  scale factor.
\end{itemize}  


\end{document}
